---
title: "owner_YumaAnderson"
output: html_document
---

Yuma Anderson

At parties, I tell people I am interested in data and communications.

__The three most important ways I organize my work are:__

* using a planner
* keeping a calendar
* cleaning my computer files

__Interesting fact about myself:__
I was in a Smithsonian traveling exhibit and a documentary.

1. Git is a tool that allows you to control different revisions of your code while Github is a service that allows you to collaborate on code.

2. Git can be used independently from Github. We use Git and Github together so we can share our work and collaborate with our classmates. The advantages to using Github are: easy collaboration, works quickly, showcases your code to future employers, and the code revision documentation is an effective way to track and organize projects. A disadvantage is that not all of the features on Github are free and it has a bit of a learning curve.

3. A repository can hold code, images, text, and is a way to manage a set of files or a project. You can make a repository of your current directory by this command:

```
mkdir [filename]
cd [filename]
git init
    ```
  
1. 
```{r}
X = c(47,34,33,65,37,NA,43,NA,11,NA,23,NA)
y = sum(is.na(X))
print(y)
    ```
2. 
```{r}
age = c(25,30,45,60,12,41)
smoker = c('T','F','T','F','F','F')
weight = c(120,137,0,168,91,142)
example_data = data.frame(age,smoker,weight)
example_data[3,3] = 150
print(example_data)
```
3. 
```{r}
NA_ratio = function(x){
return(mean(is.na(x)))
}
divide_by_total = function(x){
  return(x / sum(x, na.rm = TRUE))
}
NA_ratio(X)
divide_by_total(X)
```
4. 
```{r}
a = c(1,NA,NA,NA)
b = c(NA,3,NA,NA)
both_na = function(x,y){
  df = data.frame(x,y)
  return(nrow(subset(df, is.na(x) & is.na(y))))
}
both_na(a,b)
```

    
    